---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jaffelab

[![Travis-CI build status](https://travis-ci.org/LieberInstitute/jaffelab.svg?branch=master)](https://travis-ci.org/LieberInstitute/jaffelab)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/jaffelab/branch/master/graphs/badge.svg)](https://codecov.io/gh/LieberInstitute/jaffelab?branch=master)
[![DOI](https://zenodo.org/badge/70074284.svg)](https://zenodo.org/badge/latestdoi/70074284)

This package contains custom functions that are frequently used by the Jaffe lab. Please check the package [documentation website](http://lieberinstitute.github.io/jaffelab) for more information.

# Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `jaffelab` using the following code:

```{r, eval = FALSE}
## If needed:
if (!requireNamespace("remotes", quietly = TRUE))
   install.packages("remotes")

## Install with:
remotes::install_github('LieberInstitute/jaffelab')
```


# Citation

Below is the citation output from using `citation('jaffelab')` in R. Please 
run this yourself to check for any updates on how to cite __jaffelab__.

```{r 'citation'}
citation('jaffelab')
```

# Testing

Testing on Bioc-devel is feasible thanks to [R Travis](http://docs.travis-ci.com/user/languages/r/).
