---
title: "jaffelab quick start guide"
author: "L Collado-Torres"
date: "`r doc_date()`"
package: "`r pkg_ver('jaffelab')`"
output: 
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{jaffelab quick start guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

Quick start to using to `r Githubpkg('LieberInstitute/jaffelab')`
================================================================

```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
## Track time spent on making the vignette
startTime <- Sys.time()

## Bib setup
library('knitcitations')

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')
# Note links won't show for now due to the following issue
# https://github.com/cboettig/knitcitations/issues/63

## Write bibliography information
bibs <- c(
    BiocStyle = citation('BiocStyle'),
    devtools = citation('devtools'),
    jaffelab = citation('jaffelab'),
    knitcitations = citation('knitcitations'),
    knitr = citation('knitr')[3],
    limma = citation('limma'),
    R = citation(),
    rmarkdown = citation('rmarkdown'),
    testthat = citation('testthat')
)

write.bibtex(bibs,
    file = 'quickstartRef.bib')
bib <- read.bibtex('quickstartRef.bib')

## Assign short names
names(bib) <- names(bibs)
```



# Basics

## Install `r Githubpkg('LieberInstitute/jaffelab')`

`R` is an open-source statistical environment which can be easily modified to enhance its functionality via packages. `r Githubpkg('LieberInstitute/jaffelab')` is a `R` package available via GitHub. `R` can be installed on any operating system from [CRAN](https://cran.r-project.org/) after which you can install `r Githubpkg('LieberInstitute/jaffelab')` by using the following commands in your `R` session:

```{r 'installpkg', eval = FALSE}
## If needed:
# install.packages('devtools')

library('devtools')
install_github('LieberInstitute/jaffelab')
```

## Required knowledge

`r Githubpkg('LieberInstitute/jaffelab')` is based on many other packages and in particular in those that have implemented the infrastructure needed for dealing with RNA-seq data. TODO

If you are asking yourself the question "Where do I start using Bioconductor?" you might be interested in [this blog post](http://lcolladotor.github.io/2014/10/16/startBioC/#.VkOKbq6rRuU).

## Asking for help

As package developers, we try to explain clearly how to use our packages and in which order to use the functions. But `R` and `Bioconductor` have a steep learning curve so it is critical to learn where to ask for help. The blog post quoted above mentions some but we would like to highlight the [Bioconductor support site](https://support.bioconductor.org/) as the main resource for getting help for Bioconductor packages. For `r Githubpkg('LieberInstitute/jaffelab')` please post issues in GitHub. However, please note that if you want to receive help you should adhere to the [posting guidlines](http://www.bioconductor.org/help/support/posting-guide/). It is particularly critical that you provide a small reproducible example and your session information so package developers can track down the source of the error.

## Citing `r Githubpkg('LieberInstitute/jaffelab')`

We hope that `r Githubpkg('LieberInstitute/jaffelab')` will be useful for your research. Please use the following information to cite the package and the overall approach. Thank you!

```{r 'citation'}
## Citation info
citation('jaffelab')
```

# Reproducibility

The `r Githubpkg('LieberInstitute/jaffelab')` package `r citep(bib[['jaffelab']])` was made possible thanks to:

* R `r citep(bib[['R']])`
* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('devtools')` `r citep(bib[['devtools']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('knitr')` `r citep(bib[['knitr']])`
* `r Biocpkg('limma')` `r citep(bib[['limma']])`
* `r CRANpkg('rmarkdown')` `r citep(bib[['rmarkdown']])`
* `r CRANpkg('testthat')` `r citep(bib[['testthat']])`


Code for creating the vignette

```{r createVignette, eval=FALSE}
## Create the vignette
library('rmarkdown')
system.time(render('jaffelab-quickstart.Rmd', 'BiocStyle::html_document'))

## Extract the R code
library('knitr')
knit('jaffelab-quickstart.Rmd', tangle = TRUE)
```

```{r createVignette2}
## Clean up
file.remove('quickstartRef.bib')
```

Date the vignette was generated.

```{r reproduce1, echo=FALSE}
## Date the vignette was generated
Sys.time()
```

Wallclock time spent generating the vignette.

```{r reproduce2, echo=FALSE}
## Processing time in seconds
totalTime <- diff(c(startTime, Sys.time()))
round(totalTime, digits=3)
```

`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library('devtools')
options(width = 120)
session_info()
```

# Bibliography

This vignette was generated using `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
with `r CRANpkg('knitr')` `r citep(bib[['knitr']])` and `r CRANpkg('rmarkdown')` `r citep(bib[['rmarkdown']])` running behind the scenes.

Citations made with `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`.

```{r vignetteBiblio, results = 'asis', echo = FALSE, warning = FALSE}
## Print bibliography
bibliography()
```
